Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-11-09 longSC.tex
changed the place of figures

\begin{figure}[htbp]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
        \label{fig:Figure_1}
              \end{center}
\end{figure}

@@

The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which are taken from the recent publication~\cite{ALICE:2016kpq}. The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.
The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)).
In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller that SC(3,2).

@@

\begin{figure}[p]
	\begin{center}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts (left) and results of normalized SC(3,2) and SC(4,2) (right). The upper panels show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the bottom panels are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$. Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure}

@@

The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.  All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2). 
On the other hand, among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions. NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations and cannot be described by these models quantitively.
However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parametrizations.
Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions. Because the Glauber initial condition with $\eta/s=0.20$ can be ruled out, we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.

\begin{figure}[!p]
	\begin{center}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings. Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines. Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
         \label{fig:Figure_3}
        \end{center}   
 \end{figure}

@@

In the case of SC(4,2), the string melting AMPT model can fairly well describe the data while the default model underestimates it.
NSC(4,2) is slightly overestimated by the same setting which can describe SC(4,2) but the default AMPT model can describe the data better.
The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering makes NSC(4,2) slightly smaller.
It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT models.

\begin{figure}[p]
	\begin{center}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT simulations. Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
        \label{fig:Figure_4}
        \end{center}   
 \end{figure}

@@

\begin{figure}[htbp]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
              \end{center}
        \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations. The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}. This will be replaced with new figures once we have the calculations for Harri}
        \label{fig:Figure_5}
\end{figure}

@@

\begin{figure}[p]
	\begin{center}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines. Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
        \label{fig:Figure_6}
        \end{center}   
 \end{figure}

@@

\begin{figure}[p]
	\begin{center}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT simulations. Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
        \label{fig:Figure_7}
        \end{center}   
 \end{figure}

\pagebreak
\subsection{Transverse Momentum Dependence of Low Order Harmonic Correlations}
\label{sec:ptdepsc}

It can be seen in Fig.~\ref{fig:Figure_2} that the $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. 
In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
These observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2) simultaneously.
In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $p_{\rm T}$ dependence than the data.
As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $p_{\rm T}$ dependence are observed.
When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength get weaker by the hadronic rescattering.
This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out~\cite{Teaney:2012ke,Niemi:2015qia}.
\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}

\begin{figure}[htbp]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
              \end{center}
             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
             \label{fig:Figure_8}
\end{figure}

>>>>

@@

The centrality dependence of the higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are presented in Fig.~\ref{fig:Figure_1} and compared to the lower order harmonic correlations (SC(4,2) and SC(3,2)) which are taken from the recent publication~\cite{ALICE:2016kpq}. The correlation between $v_3$ and $v_4$ is negative, and similarly for $v_3$ and $v_2$, while the other correlations are all positive, which reveals that $v_2$ and $v_5$, $v_3$ and $v_5$ are correlated as $v_2$ and $v_4$, while $v_3$ and $v_4$ are anti-correlated as $v_3$ and $v_2$.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

The higher order flow harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are much smaller compared to the lower order harmonic correlations (SC(3,2) and SC(4,2)).
In particular SC(5,2) is 10 times smaller than SC(4,2) and SC(4,3) is about 20 times smaller that SC(3,2).

@@

\begin{figure*}
	\begin{center}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
        	\resizebox{0.48\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
        \caption{SC(3,2) and SC(4,2) with various minimum $p_{\rm T}$ cuts (left) and results of normalized SC(3,2) and SC(4,2) (right). The upper panels show the results for minimum $p_{\rm T}$ range, $0.2<p_{\rm T}<0.7$~GeV/$c$ and the bottom panels are for minimum $p_{\rm T}$ range, $0.8<p_{\rm T}<1.5$~GeV/$c$. Note that NSC data points from each minimum $p_{\rm T}$ in a centrality percentile bin are shifted for visibility.}
        \label{fig:Figure_2}
        \end{center}   
\end{figure*}

@@

\begin{figure*}[h]
	\begin{center}
        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
        \caption{Results of  SC(3,2) and SC(4,2) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings. Three initial conditions from AMPT, MC-KLN, and MC-Glauber  are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosities ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines. Upper panels are the result of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
         \label{fig:Figure_3}
        \end{center}   
 \end{figure*}

The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.  All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2). 
On the other hand, among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions. NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations and cannot be described by these models quantitively.
However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parametrizations.
Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions. Hence the Glauber initial condition with $\eta/s=0.20$ can be ruled out. We come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.

\begin{figure*}[!]
	\begin{center}
        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
        	\resizebox{0.45\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
        \caption{Results of  SC(3,2) and SC(4,2) are compared to various AMPT simulations. Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
        \label{fig:Figure_4}
        \end{center}   
 \end{figure*}

@@

In the case of SC(4,2), the string melting AMPT model can fairly well describe the data while the default model underestimates it.
NSC(4,2) is slightly overestimated by the same setting which can describe SC(4,2) but the default AMPT model can describe the data better.
The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering makes NSC(4,2) slightly smaller.
It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between the AMPT models and the data as it was demonstrated for SC(3,2).
Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT models.

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
              \end{center}
        \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations. The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}. This will be replaced with new figures once we have the calculations from Harri Niemi et. al~\cite{Niemi:2015qia}.}
        \label{fig:Figure_5}
\end{figure*}

@@

\begin{figure*}[!]
	\begin{center}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines. Upper panels are the results of SC$(m,n)$ and lower panels are the results of NSC$(m,n)$.}
        \label{fig:Figure_6}
        \end{center}   
 \end{figure*}

 \begin{figure*}[h]
	\begin{center}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) are compared to various AMPT simulations. Upper panels are the results of SC$(m,n)$ and the lower panels are the results of NSC$(m,n)$. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
        \label{fig:Figure_7}
        \end{center}   
 \end{figure*}

@@

\subsection{Transverse Momentum Dependence of Low Order Harmonic Correlations}
\label{sec:ptdepsc}

It can be seen in Fig.~\ref{fig:Figure_2} that the $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. 
In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.

\begin{figure}[p]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
              \end{center}
             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
             \label{fig:Figure_8}
\end{figure}

NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
These observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2) simultaneously.
In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $p_{\rm T}$ dependence than the data.
As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $p_{\rm T}$ dependence are observed.
When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength get weaker by the hadronic rescattering.
This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out~\cite{Teaney:2012ke,Niemi:2015qia}.
\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}
